\section{System Architecture}

The NCS-OS architecture is composed of four major structural components:
\begin{itemize}
    \item Sovereignty Stack (L0--L4)
    \item Governance Cascades (Bottom-Up and Top-Down)
    \item Cognitive Kernel
    \item Structural Topology
\end{itemize}

Each component is defined in modular JSON form, compiled into a unified IR, and rendered into infographic figures. This section describes the purpose and structure of each architectural element.

\subsection{Sovereignty Stack}
The sovereignty stack consists of five layers (L0--L4), each representing a distinct mode of civilizational operation. These layers form the vertical backbone of the NCS-OS and define the system's hierarchical structure.

\subsection{Governance Cascades}
Cascades describe the directional flows between layers. Bottom-up cascades represent emergent influence, while top-down cascades represent directive governance. Together, they form a bidirectional sovereignty dynamic.

\subsection{Cognitive Kernel}
The cognitive kernel defines the system's functional core, including APIs, functions, and constraints. It provides the computational logic that governs interactions across layers and cascades.

\subsection{Structural Topology}
Topology specifies the geometric and relational structure of the system. It includes nodes, edges, and domains that define how sovereignty components are spatially and logically arranged.

\subsection{Integration Pipeline}
The architecture is operationalized through the NCS-OS pipeline:
\begin{center}
modules $\rightarrow$ compiler $\rightarrow$ renderer $\rightarrow$ manuscript
\end{center}

This pipeline ensures that structural definitions are transformed into visual figures and integrated into the final scientific document.
